Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-13 paper/main.tex
notes/text at the end of result section

\todo[inline]{following phrasing might be strange but necessary to delineate
from Huth (2016); good voxel-wise semantic modeling regarding places in PPA but
imo that does not say anything about excitation/inhibition; interestingly Huth
mentions PPA during talks but it is not discussed in any paper and despite being
promised none of his group came up with a paper regarding that topic}
% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between stimulus features of spoken
language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces  (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain their audiences and
to capture attention free from any perceptual or behavioral task.
% AO annotation
Thus for the analysis of the AO data, we extended an publicly available
annotation of speech \citep{haeusler2020speechanno} by further annotating words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
comprise not just words that describe an abstract location (e.g. ``in
Greenbow'') or a setting as whole (e.g. ``the platoon wades through a rice
field'', ``in a disco''). They also comprise words that could count as a member
of another categories in case the narrator uses these words to indicate a switch
from one setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.  Slices were oriented to include the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs. The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.\todo{references to bib}

% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time,
\unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction
factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain. This automatic slice
positioning procedure was identical in the AV and VIS study, and yielded a
congruent geometry across paradigms.

@@

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations
(s. \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.\todo{sounds meh but
don't know how do write it better}

@@

% we did a couple of contrasts and why
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental findings.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
%
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

% intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for a couple of reasons and thus are not
included in the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``black and white film
recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
would be perceptually richer,
% hierarchical categories
(b) They also comprise words that could count as a member of another categories
in case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near and old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.\todo{cf. contrast that uses
cuts but in AO stimulus}
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.

@@

% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.\todo{cf. contrast that uses cuts but in AO stimulus}

@@

% intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).

@@

% the contrast in detail
The primary $t$-contrast for the audio-description (\texttt{geo, groom > all
non-geo}) that we used to isolate the PPA yielded six significant clusters (see
Table \ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% PPA
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% location
More specifically, the clusters of the current analysis are at the borders of
the posterior parahippocampal cortex, the occipital and temporal fusiform gyrus
and lingual gyrus \todo{the clusters are small but that's what the
Harvard-Oxford Atlas suggests, clusters are at the border of the reported areas;
cf. location of PPA in the introduction clusters}.
% precuneus
Additionally , two additional clusters are located in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, the contrast yielded two homologous clusters in the superior lateral
occipital cortex.
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. Tables for just the ``primary contrast'', seems more appropriate}

@@

% results
The overlap of significant clusters of the eight contrast for the
audio-description, and five contrasts computed for the movie can be found in
Figure \ref{fig:stability-slices}.
% results in PPA
In the analysis of the AO stimulus, six of eight contrasts show significant
bilateral clusters in anterior regions of the group PPA
overlap.\todo[inline]{temporal occipital fusiform gyrus according to
Harvard-Oxford Cortical Structural Atlas}
% Precuneus = retrosplenial cortex ?
Seven of eight contrasts show bilaterally significant clusters in the
retrosplenial region (and ventral precuneus).
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.
% individual results
Notably, we chose one contrast to look into individual results of all subjects
but individually a contrast different from the primary contrast might lead to
better individual localization results.
% transverse occipital sulcus
\todo[inline]{transverse occipital sulcus / occipital place area? in 6 of 8
contrasts}
% confounds
but confounds: right superior temporal gyrus (4 contrasts); left superior
temporal gyrus (3 contrasts); some prefrontal clusters that show up in two
contrasts
% control in AO contrasts
\todo[inline]{control contrast essentially almost all none results; s. comments}

@@

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% control AV
\todo[inline]{control in AV stim: se\_new > se\_old (nouns in AV stim): LOC
(l/r), right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)}

@@

\subsubsection{AV stimulus}
% location
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex) \todo{what overlaps with group ROI?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Hence, further studies focusing on visual perception should annotate and model
visual features of naturalistic stimuli more rigorously.
\todo[inline]{concluding statement to cross-modality of results?}

>>>>

\todo[inline]{following phrasing might be strange but necessary to delineate
from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
but imo that does not say anything about excitation/inhibition; interestingly
Huth mentions PPA during talks but it is not discussed in any paper and despite
being promised none of his group came up with a paper regarding that topic}
% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between stimulus features of spoken
language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces  (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain their audiences and
to capture attention free from any perceptual or behavioral task.
% AO annotation
Thus for the analysis of the AO data, we extended an publicly available
annotation of speech \citep{haeusler2020speechanno} by further annotating words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
\todo[inline]{compare the following with Methods: AO contrasts \& Discussion}
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
comprise not just words that describe an abstract location (e.g. ``in
Greenbow'') or a setting as whole (e.g. ``the platoon wades through a rice
field'', ``in a disco''). They also comprise words that could count as a member
of another categories in case the narrator uses these words to indicate a switch
from one setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.  Slices were oriented to include the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs. The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]\todo{references to
bib if this paragraph stays in the paper}. Auxiliary scans for slice alignment
and motion- and distortion-correction were performed at the beginning of the
first fMRI recording session and also after the break at the start of the
recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain. This automatic slice
positioning procedure was identical in the AV and VIS study, and yielded a
congruent geometry across paradigms.

@@

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
\ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo{sounds meh but don't know how do write it better; results of correlations
are given here already; maybe the short discussion (cf. very beginning of
discussion) of these correlation could be put here too which will saves space in
the main text; but mixing methods/results/discussion is not absolutely "clean"}

@@

% we did a couple of contrasts and why
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental findings.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

\todo[inline]{compare the following with annotation \& Discussion}
% intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for a couple of reasons and thus are not
included in the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``black and white film
recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
would be perceptually richer,
% hierarchical categories
(b) They also comprise words that could count as a member of another categories
in case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near and old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.
cuts but in AO stimulus}
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.

% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.\todo{all essentially almost null results}

@@

@@

% intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).
\todo[inline]{all null results; except cope 10 (nouns of narrator but in movie):
right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
lobe).

@@

% the contrast in detail
The primary $t$-contrast for the audio-description (\texttt{geo, groom > all
non-geo}) that we used to isolate the PPA yielded six significant clusters (see
Table \ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% PPA
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% location
More specifically, the clusters of the current analysis are at the borders of
the posterior parahippocampal cortex, the occipital and temporal fusiform gyrus
and lingual gyrus \todo{the clusters are small but that's what the
Harvard-Oxford Atlas suggests, clusters are at the border of the reported areas;
cf. location of PPA in the introduction clusters}.
% precuneus
Additionally, two additional clusters are located in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, the contrast yielded two homologous clusters in the superior lateral
occipital cortex.
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. Tables for just the ``primary contrast'', seems more appropriate; the
level of details explained depends on the discussion; atm moment I feel it
should be discussed more than expected; hence, following some notes as to dos}

@@

@@

% results
The overlap of significant clusters of the eight contrast for the
audio-description, and five contrasts computed for the movie can be found in
Figure \ref{fig:stability-slices}.
% results in PPA
In the analysis of the AO stimulus, six of eight contrasts show significant
bilateral clusters in anterior regions of the group PPA
overlap.\todo[inline]{temporal occipital fusiform gyrus according to
Harvard-Oxford Cortical Structural Atlas}
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.
% individual results
Notably, we chose one contrast to look into individual results of all subjects
but individually a contrast different from the primary contrast might lead to
better individual localization results.\todo{concluding statements often feel
like interpretation/discussion to me}

% Precuneus = retrosplenial cortex ?
\todo[inline]{Seven of eight contrasts show bilaterally significant clusters in
the retrosplenial region (and ventral precuneus)}.

% transverse occipital sulcus
\todo[inline]{transverse occipital sulcus / occipital place area? in 6 of 8
contrasts (4 bilaterally)}

% confounds
\todo[inline]{``other clusters'' (confounds?): right superior temporal gyrus (4
contrasts); left superior temporal gyrus (3 contrasts); some prefrontal clusters
that show up in two contrasts}

% control in AO contrasts
\todo[inline]{control contrast essentially almost all none results; s. comments}

@@

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.\todo{must be in posterior PPA as well}
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual
gyri.\todo[inline]{check regions and contrasts that are located outside of the
PPA; border of lingus belongs to PPA}
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.\todo{concluding statement =
interpretation/discussion?}

% control AV
\todo[inline]{control in AV stim: se\_new > se\_old (nouns in AV stim): LOC
(l/r), right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)}

@@

\subsubsection{AV stimulus}
% location
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex)\todo{which of these regions overlap
with group ROI? which regions show clusters but do not overlap with PPA?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Hence, further studies focusing on visual perception should annotate and model
visual features of naturalistic stimuli more rigorously.
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of results?}
